### 2022-06-13 manuscript.tex
Merge pull request #234 from colebrookson/main [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1498796835167c3f7d1f4135eca274b5e7d6346c.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/1498796835167c3f7d1f4135eca274b5e7d6346c/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2489350199

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/ea3d52568405d25c555daffaef4bbf5a40954c92/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/ea3d52568405d25c555daffaef4bbf5a40954c92}{SORTEE-Github-Hackathon/manuscript@ea3d525}
on June 10, 2022.

@@

\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor and Francis Group, 2019).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{Dawson, C. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/1498796835167c3f7d1f4135eca274b5e7d6346c/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/1498796835167c3f7d1f4135eca274b5e7d6346c}{SORTEE-Github-Hackathon/manuscript@1498796}
on June 13, 2022.

@@

\leavevmode\vadjust pre{\hypertarget{ref-QqMezOMg}{}}%
\CSLLeftMargin{25. }
\CSLRightInline{Xie, Y., Allaire, J. J. \& Grolemund, G. \emph{R Markdown: the definitive guide}. (CRC Press, Taylor \& Francis Group, 2019).}

@@

\leavevmode\vadjust pre{\hypertarget{ref-MXxgZJ45}{}}%
\CSLLeftMargin{28. }
\CSLRightInline{Dawson, C. \& Straub, B. \emph{Building tools with GitHub: customize your workflow}. (O'Reilly, 2016).}
